### 2015-11-04 CVPR16/Source/abstract.tex

\begin{abstract}
We propose a model for representation of objects so that points can be
probabilistically  associated to the tracklets while accounting for occlusion.
We compare our approach against state of the art motion segmentation methods.
\end{abstract}

>>>>

\begin{abstract}
We propose a novel model for representing objects so that point tracks can be
probabilistically  associated with objects while accounting for object occlusions.
We compare our approach against state-of-the-art motion segmentation methods.
\end{abstract}

### 2015-11-04 CVPR16/Source/experiments.tex

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of input point tracks. Numbers on y-axis represent data sequence numbers in KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 29.3 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 16.4 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association errors on different sets of input point tracks over all sequences of KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{table}

>>>>

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of input point tracks. Numbers on y-axis represent data sequence numbers in KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 30.1 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 17.7 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association errors on different sets of input point tracks over all sequences of KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{table}
